---
title: "Assign FWI to DOB"
author: "Anna Talucci"
date: '2022-05-19'
output: html_document
---


# Overview
Working through the fire weather model to convert DOB for tweedsmuir perimeter to FWI. This is adapted from the orginal r script that was included in the data send.

Day of burnratsers were provided bt Canadian  Forest Service.




# Required Packages
```{r eval=FALSE, include=FALSE}
library(raster)
library(rgdal)
```


# Make list of DOB ascii files
```{r eval=FALSE, include=FALSE}
list1<-list.files(path='.',pattern=".asc") ######### make a list of the burn date ascii files
list1<-list1[-4] # "extra"
```

```{r, include=FALSE}
library(sp) # spatial data
library(rgdal) # geospatial data
library(raster) # deals with rasters
library(landsat) # processes landsat images
library(rgeos) # GIS Geometry
library(foreign) # deals with dbf files
library(SDMTools) #Species distribution model tools for patch metrics
library(dplyr)
```

# Tweed: DOB to FWI

```{r}
twr = raster("../data/dob/R10252_2013_dob.tif")

cellStats(twr, 'min')#returns the minimum cell value -439.9731
cellStats(twr, 'max')#returns the maximum cell value 1141.094

summary(twr)
structure(twr)
```


# FWI Data

```{r}
weather = read.csv("../data/weather-station-data/AllFires_dailyweather_16August2017.csv", header=TRUE, sep = ",", strip.white = TRUE)
head(weather)
```

## DoB Data
Selecte fire event R10252_2013 to see Day of Burn (DOB) range.

```{r}
weather %>% filter(Fire_id == "R10252_2013") %>%
  dplyr::select(Fire_id, Burndate, fwi)
```

# Reclassify from DOB to FWI
To reclassify the raster, first, define matrix with 3 columns - from, to, becomes. 

```{r}
m = c(255.0,255.9,22.2, 256.0,256.9,22.0, 257.0,257.9,21.3, 258.0,258.9,24.0, 259.0,259.9,28.9) 
rclmatrix = matrix(m, ncol=3, byrow=TRUE) 
```

Then, apply the function to reclassify and write raster to save the classified raster.

```{r}
twclassfwi = reclassify(twr, rclmatrix, right = FALSE, 
                       filename="../outputs/rasters/fwi/tw_fwi", format="GTiff",  
                       overwrite=TRUE)
```

```{r}
twfwi = raster("../outputs/rasters/fwi/tw_fwi.TIF")
structure(twfwi)
plot(twfwi)

cellStats(twfwi, min)
cellStats(twfwi, max)
cellStats(twfwi, median)
```


**THE END**