---
title: "Select hotspots within fire perimeters"
author: "Anna Talucci"
date: '2022-05-31'
output: html_document
---

# Overview

https://gis.stackexchange.com/questions/287988/kriging-example-with-sf-object

https://rpubs.com/nabilabd/118172


https://rpubs.com/nabilabd/134781

https://stackoverflow.com/questions/47171710/create-a-grid-inside-a-shapefile

https://stackoverflow.com/questions/64897321/cellsize-in-sfst-make-grid-seems-to-not-relate-to-map-units

## Steps 
1. Buffer perimeters by
2. Select points within perimeters
3. Apply kriging at 30 m resolution?
4. Convert points to raster at 30 m resolution


# Packages

```{r}
library(sf)
library(sp)
library(gstat)
library(tidyverse)
library(lubridate)
library(stars)
library(raster)
```

# Data

```{r}
fp = st_read("../data/NWTSubsetFireperimeters/NWT10SampleFires2014.shp", "NWT10SampleFires2014")
```


```{r}
lrgfire = st_read("../data/NWTSubsetFireperimeters/NWTModerateFire2014.shp", "NWTModerateFire2014")
```

```{r}
smfire = st_read("../data/NWTSubsetFireperimeters/NWTsmallFire2014.shp", "NWTsmallFire2014")
```

```{r}
modis = st_read("../data/hotspots/DL_FIRE_M-C61_271571/fire_archive_M-C61_271571.shp", "fire_archive_M-C61_271571")
```


```{r}
viirs = st_read("../data/hotspots/DL_FIRE_SV-C2_271573/fire_archive_SV-C2_271573.shp", "fire_archive_SV-C2_271573")
```

# Projections
## View projections for shapefiles
```{r}
st_crs(fp)
```

```{r}
st_crs(modis)
```

```{r}
st_crs(viirs)
```

## Define projection variables

```{r}
projection = ("+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-96 +x_0=0 +y_0=0 +datum=NAD83 +units=m +no_defs" )
```

## Reproject shapefiles to equal area

```{r}
fp = st_transform(fp, projection)

st_crs(fp)
```

```{r}
smfire = st_transform(smfire, projection)

st_crs(smfire)
```
Reproject hotspots to the same projections as the fire perimeters

```{r}
modis_proj = st_transform(modis, projection)

st_crs(modis_proj)
```
```{r}
modis_proj
```

```{r}
viirs_proj = st_transform(viirs, projection)

st_crs(viirs_proj)
```


# Processing

## Buffer fire perimeters
```{r}
plot(st_geometry(fp), col = "red")
```


```{r}
fp_buf <- st_buffer(fp, dist = 1000)
```

```{r}
smfire_buf <- st_buffer(smfire, dist = 1000)
```

```{r}
plot(st_geometry(viirs_proj), col="gray")
plot(st_geometry(fp_buf), col = "red", add = TRUE)

```

## Select points 
Not sure if this is the right function
```{r}
modis_smfire = st_intersection(modis_proj, smfire_buf)

modis_smfire
```

```{r}
plot(st_geometry(smfire_buf))
plot(st_geometry(modis_smfire), add=TRUE)
```
```{r}
viirs_smfire = st_intersection(viirs_proj, smfire_buf)

viirs_smfire
```

```{r}
plot(st_geometry(smfire_buf))
plot(st_geometry(viirs_smfire), add=TRUE)
```
## Make Gird 

```{r}
grid30 <- smfire_buf %>% 
  st_make_grid(cellsize = 30, what = "centers") %>% # grid of points
  st_intersection(smfire_buf)   
```

```{r}
grid500 <- smfire_buf %>% 
  st_make_grid(cellsize = 500, what = "centers") %>% # grid of points
  st_intersection(smfire_buf)   
```

```{r}
grid375 <- smfire_buf %>% 
  st_make_grid(cellsize = 375, what = "centers") %>% # grid of points
  st_intersection(smfire_buf)   
```

```{r}
plot(grid30)
```


## Add Julian date
```{r}
modis_pts = modis_smfire %>% mutate(julianDate = yday(ACQ_DATE))
viirs_pts = viirs_smfire %>% mutate(julianDate = yday(ACQ_DATE))
```

```{r}
min(modis_pts$julianDate)
max(modis_pts$julianDate)
```

```{r}
min(viirs_pts$julianDate)
max(viirs_pts$julianDate)
```

## Combine MODIS and VIIRS and Run kriging

```{r}
head(modis_pts)
```

```{r}
head(viirs_pts)
```

```{r}
all_pts = rbind(modis_pts, viirs_pts)
all_pts
```


## Fit variogram

```{r}
modis_vgm <- variogram(julianDate~1, modis_pts)

class(modis_vgm)

modis_fit <-
  fit.variogram(modis_vgm, model = vgm(1,"Lin",900,1)) # fit model

# vgm() list of models

plot(modis_vgm, modis_fit)
```

```{r}
viirs_vgm <- variogram(julianDate~1, viirs_pts)

class(viirs_vgm)

viirs_fit <-
  fit.variogram(viirs_vgm, model = vgm(1,"Lin",900,1)) # fit model

# vgm() list of models

plot(viirs_vgm, viirs_fit)
```

```{r}
allpts_vgm <- variogram(julianDate~1, all_pts)

class(allpts_vgm)

allpts_fit <-
  fit.variogram(allpts_vgm, model = vgm(1,"Lin",900,1)) # fit model

# vgm() list of models

plot(allpts_vgm, allpts_fit)
```

## Apply Kriging

```{r}
modis_kriged <- krige((julianDate) ~ 1, modis_pts, grid500, model=modis_fit)
```

```{r}
modis_kriged
```
## Rasterize sf object
```{r}
(x = st_rasterize(modis_kriged, st_as_stars(st_bbox(modis_kriged), values = var1.pred)))
```

```{r}

plot(x, axes = TRUE)
```

```{r}
viirs_kriged <- krige((julianDate) ~ 1, viirs_pts, grid375, model=viirs_fit)
```

```{r}
viirs_kriged
```

```{r}
allpts_kriged <- krige((julianDate) ~ 1, all_pts, grid375, model=allpts_fit)
```

```{r}
allpts_kriged
```

## Plot kriged data

```{r}
ggplot(data = modis_kriged) +
    geom_sf(aes(color = var1.pred), size = 1)

```
```{r}
str(modis_kriged)
```
```{r}
ggplot(data = viirs_kriged) +
    geom_sf(aes(color = var1.pred), size = 1)

```

```{r}
ggplot(data = allpts_kriged) +
    geom_sf(aes(color = var1.pred), size = 1)

```

```{r eval=FALSE, include=FALSE}
lzn.kriged %>% as.data.frame %>% rename(lon=coords.x1, lat=coords.x2) %>% 
  ggplot(aes(x=lon, y=lat)) + geom_tile(aes(fill=var1.pred)) + coord_equal() +
  scale_fill_gradient2(low="green", mid = "yellow",  high="red",midpoint = 15) +
  theme_bw()+
  geom_point(data=dt, aes(color=z), size=10)+
  geom_text(data=dt, aes(label=z), color="white")
```

## Export points for GEE
```{r}
head(modis_pts)
```

```{r}
modis_pts1 = modis_pts %>% dplyr::select(LATITUDE:BT_GID, julianDate, geometry)
```

```{r eval=FALSE, include=FALSE}

st_write(viirs_pts, "../outputs/VIIRSptsNWTsmallFire2014.shp", driver="ESRI shapefile")
```

```{r eval=FALSE, include=FALSE}

st_write(modis_pts1, "../outputs/modispoints2014.shp", driver="ESRI shapefile")
```


## Convert to raster
```{r}
head(modis_kriged)
```
```{r}
r = rasterFromXYZ(modis_kriged$map)
plot(r)
```

 xmin: -1016420 ymin: 1406252 xmax: -984259.6 ymax: 1418012
```{r}
# Convert points to sp (assumes that the sf object is called example_points)
modis_kriged_sp <- as(modis_kriged, "Spatial")
```
# Generate empty raster layer
```{r}

r <- raster(resolution = 1000, ext = extent(c(xmin= -1016420, ymin= 1406252, xmax= -984259.6, ymax= 1418012))) 
```

```{r}
plot(r)
```
# Add projection
```{r}

crs(r) <-("+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-96 +x_0=0 +y_0=0 +datum=NAD83 +units=m +no_defs" )


```
# rasterize points
```{r}
plot(modis_kriged)
```
```{r}

raster_modis = raster::rasterize(modis_kriged_sp, r, "var1.pred", fun=mean)
```

```{r}
plot(modis_raster)

```
